---
title: "Goal Tracker"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    css: styles.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DBI)
library(dplyr)
library(htmltools)
```

```{r readData, include=FALSE}
## Read in data from database
db <- dbConnect(RSQLite::SQLite(), 'goals.sqlite')
df.main <- dbReadTable(db, 'mainGoals')
df.sub <- dbReadTable(db, 'subGoals')
dbDisconnect(db)

```


Summary
==========================

```{r, echo = FALSE, eval = TRUE}

sumOut <- lapply(seq(nrow(df.main)), function(i) {
  df.subForMain <- df.sub %>% filter(refMain == df.main[i, 'refMain'])
  goals <- list(
    ## Heading
    knitr::knit_expand(text = "Row {data-height=55}"),
    knitr::knit_expand(text = "-----------------------------\n\n"), # New Row
    knitr::knit_expand(text = sprintf("\n```{r mainheader_%s}\n", df.main[i, 'refMain'])), # start r chunk
    knitr::knit_expand(text = sprintf("p(span(\"%s\", style = \"font-size: 130%%; color: blue;\"), br(), span(\"%s\", style = \"font-size: 85%%;\"))", df.main[i, 'name'], df.main[i, 'notes'])),
    knitr::knit_expand(text = "\n```\n"), # end r chunk

    ## Gauges
    knitr::knit_expand(text = "Row {data-height=200}"),
    knitr::knit_expand(text = "-----------------------------\n\n"), # New Row
    sapply(seq(nrow(df.subForMain)), function(j){
      list(
        knitr::knit_expand(text = sprintf("### SUBGOAL %s", j)), # Sub-goal gauge header
        knitr::knit_expand(text = sprintf("\n```{r mainsubgoal_%s_%sB}\n", df.subForMain[j, 'refMain'], df.subForMain[j, 'refSub'])), # start r chunk
        knitr::knit_expand(text = sprintf("gauge(%s, min = 0, max = 100, symbol = '%%', gaugeSectors(success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))", df.subForMain[j, 'percentComplete'])), # Gauge showing progress
        knitr::knit_expand(text = "\n```\n") # end r chunk
      )
    })
  )
  paste(unlist(goals), collapse = '\n') # collapse together all lines with newline separator
})

```

`r knitr::knit(text = paste(sumOut, collapse = '\n'))`


```{r, echo = FALSE, eval = TRUE}

expandSub <- function(d) {
  today <- format(Sys.Date(), '%Y-%m-%d')
  d <- transform(d, status = ifelse(!timeBound, "Not Timebound",
                                    ifelse(percentComplete == 100, "Completed",
                                           ifelse(today > end, "Overdue",
                                                  ifelse(percentComplete == 0, "Not Started", "Ongoing")))))
  d <- transform(d, valColor = ifelse(!timeBound, "DarkGrey",
                                    ifelse(percentComplete == 100, "DarkGreen",
                                           ifelse(today > end, "Crimson",
                                                  ifelse(percentComplete == 0, "CornflowerBlue", "LightGreen")))))

  lapply(seq(nrow(d)), function(i) {
    list(
      knitr::knit_expand(text = "Row"),
      knitr::knit_expand(text = "-----------------------------\n\n"), # New Row
      knitr::knit_expand(text = sprintf("### SUBGOAL %s", i)), # Sub-goal textbox header
      knitr::knit_expand(text = sprintf("\n```{r subgoal_%s_%sA}\n", d[i, 'refMain'], d[i, 'refSub'])), # start r chunk
      knitr::knit_expand(text = sprintf("p(\"%s\", class=\"goal-header\")\n", d[i, 'name'])), # Sub-goal Name
      knitr::knit_expand(text = sprintf("h5(\"%s\")\n", d[i, 'notes'])), # Sub-goal Notes
      ifelse(
        is.na(d[i, 'tags']),
        knitr::knit_expand(text = ''),
        sapply(strsplit(d[i, 'tags'], ';'), function(t) knitr::knit_expand(text = sprintf("a(class = \"label label-%s\", \"%s\")", t, t)))
      ),
      knitr::knit_expand(text = "\n```\n"), # end r chunk
      knitr::knit_expand(text = sprintf("### SUBGOAL %s", i)), # Sub-goal valuebox header
      knitr::knit_expand(text = sprintf("\n```{r subgoal_%s_%sB}\n", d[i, 'refMain'], d[i, 'refSub'])), # start r chunk
      knitr::knit_expand(text = ifelse(d[i, 'timeBound'], sprintf("valueBox(caption = '%s<br>%s', value = '%s', icon = 'fa-calendar', color = '%s')", d[i, 'start'], d[i, 'end'], d[i, 'status'], d[i, 'valColor']),
                         sprintf("valueBox(caption = ' ', value = '%s', icon = 'fa-calendar', color = '%s')", d[i, 'status'], d[i, 'valColor']))), # Valuebox
      knitr::knit_expand(text = "\n```\n"), # end r chunk
      knitr::knit_expand(text = sprintf("### SUBGOAL %s", i)), # Sub-goal gauge header
      knitr::knit_expand(text = sprintf("\n```{r subgoal_%s_%sC}\n", d[i, 'refMain'], d[i, 'refSub'])), # start r chunk
      knitr::knit_expand(text = sprintf("gauge(%s, min = 0, max = 100, symbol = '%%', gaugeSectors(success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))", d[i, 'percentComplete'])), # Goal Name
      knitr::knit_expand(text = "\n```\n") # end r chunk
    )
  })
}

out <- lapply(seq(nrow(df.main)), function(i) {
  
  cont <- list(
    knitr::knit_expand(text = sprintf("GOAL %s", i)), # New Page
    knitr::knit_expand(text = "============================\n\n"), # New Page
    knitr::knit_expand(text = sprintf("\n```{r maingoal_%s}\n", df.main[i, 'refMain'])), # start r chunk
    knitr::knit_expand(text = sprintf("h4(\"Name: %s\")\n", df.main[i, 'name'])), # Goal Name
    knitr::knit_expand(text = "\n```\n"), # end r chunk
    unlist(expandSub(df.sub %>% filter(refMain == df.main[i, 'refMain'])))
  )
  paste(unlist(cont), collapse = '\n') # collapse together all lines with newline separator

})

```

`r knitr::knit(text = paste(unlist(out), collapse = '\n'))`
